---
title: "Week 9, Day 2"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

* Describe the population for which you are creating the model.

* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.


$$ reg\_chg_i = \beta_0 + \beta_1 treatment + \beta_2 poverty\_n + \epsilon $$

```{r}
fit_obj <- stan_glm(data = week_9,
                  reg_chg ~ treatment*poverty_n,
                  family = gaussian(),
                  refresh = 0)

print(fit_obj, digits = 4)
```


## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?

The poverty_n value is negative, which may balance out the treatment affect based on our stan_glm result and our data.

* Describe the ideal Preceptor Table.

The ideal preceptor table would have the control, treatment, and treatment:poverty_n interaction at all time points.

* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

```{r}
new_data <- week_9 %>% 
  head(1)

pp <- posterior_predict(fit_obj, newdata = new_data)

pp %>% 
  as_tibble() %>% 
  ggplot(aes(x = `1`)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100) + 
  geom_vline(xintercept = .04, color = "blue") +
  labs(x = "Affect",
       y = "Probability",
       title = "Change in Voter Registration From Treatment") +
  scale_y_continuous(labels = scales::percent) + 
  theme_minimal()
```


* Answer the President's question.

We predict no affect of treatment at polling station 007/001, however it is possible. 


## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 


```{r}
new_data_2 <- tibble(treatment = c("local", "control"), 
       poverty_n = 2)
  

pe <- posterior_epred(fit_obj, newdata = new_data_2)



pe %>% 
  as_tibble() %>% 
  mutate(new = `1` - `2`) %>% 
  ggplot(aes(x = new)) +
  geom_histogram(aes(y = after_stat(count/sum(count))),
                 bins = 100) +
  labs(x = "Affect",
       y = "Probability",
       title = "Change in Voter Registration From Treatment") +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal()

